Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-07-17 abstract.tex
part of Ante's comment

The correlations between event-by-event fluctuations of anisotropic flow harmonic amplitudes
have been measured in $\PbPb$ collisions at $\snn=2.76$~TeV with the ALICE detector at the Large Hadron Collider. 
The results were obtained with the multiparticle correlation observables dubbed Symmetric Cumulants.
These observables are robust against biases originating from non-flow effects. 
The centrality dependence of correlations between the higher order harmonics (the quadrangular $v_4$ and pentagonal $v_5$ flow) and the lower order harmonics (the elliptic $v_2$ and triangular $v_3$ flow)
is presented. The transverse momentum dependence of correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$ is also reported. 
The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) model calculations.
The comparisons to viscous hydrodynamic models demonstrate that
the different order harmonic correlations respond differently to the initial conditions and the temperature dependence of the ratio of shear viscosity to entropy density ($\eta/s$). 
A small average value of $\eta/s$ is favored independent of specific choice of initial conditions in the models. The calculations with the AMPT initial conditions yield results closest to the measurements. 
Correlations between the magnitudes of $v_2$, $v_3$ and $v_4$ show moderate $p_{\rm T}$ dependence in mid-central collisions. This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out, which might help to understand the possible contribution of bulk viscosity in the hadronic phase of the system.
Together with existing measurements of individual flow harmonics, the presented results provide further constraints 
on initial conditions and the transport properties of the system produced in heavy-ion collisions.

>>>>

The correlations between event-by-event fluctuations of anisotropic flow harmonic amplitudes
have been measured in $\PbPb$ collisions at $\snn=2.76$~TeV with the ALICE detector at the Large Hadron Collider. 
The results were obtained with the multiparticle correlation observables dubbed Symmetric Cumulants.
These observables are robust against biases originating from nonflow effects. 
The centrality dependence of correlations between the higher order harmonics (the quadrangular $v_4$ and pentagonal $v_5$ flow) and the lower order harmonics (the elliptic $v_2$ and triangular $v_3$ flow)
is presented. The transverse momentum dependence of correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$ is also reported. 
The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) model calculations.
The comparisons to viscous hydrodynamic models demonstrate that
the different order harmonic correlations respond differently to the initial conditions and the temperature dependence of the ratio of shear viscosity to entropy density ($\eta/s$). 
A small average value of $\eta/s$ is favored independent of the specific choice of initial conditions in the models. The calculations with the AMPT initial conditions yield results closest to the measurements. 
Correlations between the magnitudes of $v_2$, $v_3$ and $v_4$ show moderate $p_{\rm T}$ dependence in mid-central collisions. This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out, which might help to understand the possible contribution of bulk viscosity in the hadronic phase of the system.
Together with existing measurements of individual flow harmonics, the presented results provide further constraints 
on initial conditions and the transport properties of the system produced in heavy-ion collisions.

### 2017-07-17 longSC.tex
part of Ante's comment

%Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle %Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-%event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}. 
The first results for new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
The new observables are particularly robust against few-particle nonflow correlations and they provide independent, complementary information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
In this article, we have extended the analysis of SC observables to higher order harmonics (up to $5^{\mathrm{th}}$ order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also present a systematic comparison to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods. The experimental setup and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. The results of the measurements are presented in Sec.~\ref{sec:results}. 
 In Sec.~\ref{sec:theory} we present comparisons to model calculations. Various models used in this article are described in Sec.~\ref{sec:theory}. Finally, Sec.~\ref{sec:summary} summarizes our findings.

@@

\section{Results}
\label{sec:results}
The centrality dependence of the higher order harmonic correlations (SC($m$,$n$) for $m$+$n$ $>$ 6) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC($m$,$n$) for $m$+$n$ $\leq$ 6) which were measured in \cite{ALICE:2016kpq}. The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated like $v_3$ and $v_2$.

@@

The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics. With well-tuned transport coefficients and decoupling temperature, and given initial conditions discussed later, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
Traditionally, the Glauber model constructs the initial entropy density with contributions from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}. In {MC-Glauber} and {MC-KLN}~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei. For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate. Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}. The detailed quantitative comparisons of the measured $v_n$ to the model calculations are provided in Appendix~\ref{sec:vn}.

%The centrality dependence of the SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short lifetime. To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
The AMPT model can be run in two main configurations, the default and the string melting model~\footnote{The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.}.
In the default version, partons are recombined with their parent strings when they stop interacting. The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}. In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}. These partons are then combined into the final state hadrons via a quark coalescence model. 
In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
The third version used in this article is based on the string melting configuration in which the hadronic rescattering phase is switched off to study its influence on the development of anisotropic flow. 
Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV. It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for the quantitative disagreement~\cite{Adam:2016nfo}. The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}. The quantitative comparisons of the measured $v_n$ to various AMPT configurations are provided in Appendix~\ref{sec:vn}.

>>>>

%Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle %Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-%event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}. 
The first results for new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
The new observables are particularly robust against few-particle nonflow correlations and they provide independent, complementary information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
In this article, we have extended the analysis of SC observables to higher order harmonics (up to $5^{\mathrm{th}}$ order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also present a systematic comparison to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods. The experimental setup and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. The results of the measurements are presented in Sec.~\ref{sec:results}. 
 In Sec.~\ref{sec:theory} we present comparisons to model calculations. Various models used in this article are described in Sec.~\ref{sec:theory}. Finally, Sec.~\ref{sec:summary} summarizes our new results.

@@

\section{Results}
\label{sec:results}
The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(3,2) and SC(4,2)) which were measured in \cite{ALICE:2016kpq}. The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated like $v_3$ and $v_2$.

@@

The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics. With well-tuned transport coefficients and decoupling temperature, and given initial conditions discussed next, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
Traditionally, the Glauber model constructs the initial entropy density with contributions from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}. In {MC-Glauber} and {MC-KLN}~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei. For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and spatial coordinates. Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}. The detailed quantitative comparisons of the measured $v_n$ to the model calculations are provided in Appendix~\ref{sec:vn}.

%The centrality dependence of the SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short lifetime. To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
The AMPT model can be run in two main configurations, the default and the string melting model~\footnote{The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.}.
In the default version, partons are recombined with their parent strings when they stop interacting. The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}. In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}. These partons are then combined into the final state hadrons via a quark coalescence model. 
In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
The third version used in this article is based on the string melting configuration in which the hadronic rescattering phase is switched off to study its influence on the development of anisotropic flow. 
Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV. It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for this quantitative disagreement~\cite{Adam:2016nfo}. The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}. The quantitative comparisons of the measured $v_n$ to various AMPT configurations are provided in Appendix~\ref{sec:vn}.
